Enhancement of SDR in Thessaloniki

### 2024-06-12 GHI_enh_04_investigate.tex
Commit 2024-06-11 13:11
Commit 2024-06-11 20:14
Commit 2024-06-11 23:11
Commit 2024-06-12 11:11
Commit 2024-06-12 12:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-10}

@@

\caption{ - empty caption - }\label{fig:groups-1}
\end{figure}

{[}1{]} 0.8092946

@@

@@

\caption{ - empty caption - }\label{fig:groups-3}
\end{figure}
\begin{figure}[H]

\caption{ - empty caption - }\label{fig:groups-4}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-6}
\end{figure}

@@

@@

\begin{verbatim}
2024-06-10 09:43:05.7 athan@tyler GHI_enh_04_investigate.R 3.417696 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-12}

@@

\caption{ - empty caption - }\label{fig:groups-1}
\end{figure}
\begin{figure}[H]

\begin{verbatim}
Attaching package: 'scales'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:viridis':

    viridis_pal
\end{verbatim}

\begin{verbatim}
Warning: The dot-dot notation (`..count..`) was deprecated in ggplot2 3.4.0.
i Please use `after_stat(count)` instead.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

\caption{ - empty caption - }\label{fig:groups-3}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-4}
\end{figure}

@@

@@

\caption{ - empty caption - }\label{fig:groups-6}
\end{figure}
\begin{figure}[H]

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9}

\caption{ - empty caption - }\label{fig:groups-9}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10}

\caption{ - empty caption - }\label{fig:groups-10}
\end{figure}

@@

\begin{verbatim}
2024-06-12 08:50:47.4 athan@tyler GHI_enh_04_investigate.R 1.594768 mins
\end{verbatim}
